Detecting distributional differences between temporal granularities for exploratory time series analysis

### 2021-05-20 paper/main.Rmd
deleted application 2 pictures and a table - fixing pg numbers

@@

# Normalization for the number of comparisons {#sec:norm-wpd}

@@

```{r tab-demography}
demography <- tibble(id = c(1, 2, 3, 4, 5,6, 7, 8), 
       profession = c("academia", "mixed", "industry", "industry", "mixed", "mixed", "academia", "industry"),
       total_members = c(2, 3, 5, 5, 2, 2, 2, 6),
       kids = c("no", "no", "yes", "yes", "no", "no", "no", "yes"),
       old_parents = c("no", "yes", "yes", "yes", "no", "no", "no", "yes"),
       PhD_student = c("no", "yes", "no", "no", "yes", "yes", "yes", "no"))

@@

```{r linear-scale-8, fig.cap = "Electricity demand for eight households is shown in different facets from Jul-19 to Dec-19 in Fig a and it has been zoomed in for Sep-19 in Fig b, where a week in Sep-19 has been highlighted. From the scales of Fig a, it is apparent that these households vary in consumption levels, but all their periodic patterns have been squeezed with this representation. In fig b, we can see some weekly patterns for the entire period and daily patterns for the highlighted week and there could be some other patterns visible in terms of peaks and troughs, but it is not clear if they are regular or significant.", fig.height=8}
library(scales)
library(tidyquant)
library(gghighlight)
library(lubridate)

@@

```{r raw-nqt-8, fig.height = 5, fig.cap="The raw density of the half-hourly demand for the eight households is shown in Fig a. Fig b shows the normal-score-transformed half-hourly demand for the same households which has resulted in more symmetric distribution of half-hourly demand."}
elec_raw <- elec %>% 
  ggplot() +
  geom_density(aes(x = kwh)) +
  facet_wrap(~id, scales = "free_y", ncol = 1) +
  xlab("demand (in kwh)") + ggtitle("a") +
  theme(
        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))

>>>>

## Properties of $wpd$

@@

# Adjusting for the number of comparisons {#sec:norm-wpd}

@@

```{r tab-demography, eval = FALSE}
demography <- tibble(id = c(1, 2, 3, 4, 5,6, 7, 8), 
       profession = c("academia", "mixed", "industry", "industry", "mixed", "mixed", "academia", "industry"),
       total_members = c(2, 3, 5, 5, 2, 2, 2, 6),
       kids = c("no", "no", "yes", "yes", "no", "no", "no", "yes"),
       old_parents = c("no", "yes", "yes", "yes", "no", "no", "no", "yes"),
       PhD_student = c("no", "yes", "no", "no", "yes", "yes", "yes", "no"))

@@

```{r linear-scale-8, fig.cap = "Electricity demand for eight households is shown in different facets from Jul-19 to Dec-19 in Fig a and it has been zoomed in for Sep-19 in Fig b, where a week in Sep-19 has been highlighted. From the scales of Fig a, it is apparent that these households vary in consumption levels, but all their periodic patterns have been squeezed with this representation. In fig b, we can see some weekly patterns for the entire period and daily patterns for the highlighted week and there could be some other patterns visible in terms of peaks and troughs, but it is not clear if they are regular or significant.", fig.height=8, eval = FALSE}
library(scales)
library(tidyquant)
library(gghighlight)
library(lubridate)

@@

```{r raw-nqt-8, fig.height = 5, fig.cap="The raw density of the half-hourly demand for the eight households is shown in Fig a. Fig b shows the normal-score-transformed half-hourly demand for the same households which has resulted in more symmetric distribution of half-hourly demand.", eval = FALSE}
elec_raw <- elec %>% 
  ggplot() +
  geom_density(aes(x = kwh)) +
  facet_wrap(~id, scales = "free_y", ncol = 1) +
  xlab("demand (in kwh)") + ggtitle("a") +
  theme(
        strip.text = element_text(size = 10, margin = margin(b = 0, t = 0)))
